MLCommons Earthquake Science Benchmark

### 2022-02-25 paper-capstone-earthquake.tex
Updates from Overleaf

\TODO{This section is in progress! Enter Energy Weighted Quantities
  equations picture below}

This function maximizes the largest earthquake energy values for the 2
week period.  Magnitude averaged over the bin All input values and
predictions are independently normalized and have a maximum modulus of
1 over all space and time values. \cite{fox2022aiforscience}

@@

The data being used is the Southern California location data, between
32 to 36 lat -120 to -114 long. The data is recorded between
1950-2020. Each location point is is 0.1 by 0.1 degrees or ll km by ll
km in size or 2400 points in total. The points are then put into
spatial bag which are based on a bunch of different location points,
necessarily nearby spatially. Each location point has a time series
associated with it. The time series data holds magnitude, depth,
spatial position, and time. \cite{fox2021earthquake}

The data was accumulated into 2 week samples using energy-based
averaging, the log loss equation.

@@

\begin{table*}[!ht]
\caption{Gregors MNIST Benchmarks}\label{tab:mnist}
    \centering
      \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
    \hline
        Machine & real & user & sys & Driver & CUDA & GPU & \makecell{Date CPU \\released} & CPU & \makecell{Date CPU \\released} \\ \hline
        Gregors Machine & 0m11.534s & 0m13.914s & 0m05.186s & 510.47.03 & 11.6 & Gigabyte RTX3070 TI & May 31, 2021 & AMD 5950X & Nov 2020 \\ \hline
        Fox DGX & 0m19.987s & 5m12.991s & 0m49.266s & 450.142.00 & 11.0 & NVIDIA A100 80GB & & AMD EPYC 7742 64-Core & Aug 2019 \\ \hline
        Rivanna A100 & 0m29.263s & 0m14.585s & 0m7.399ss & 470.82.01 & 11.4 & NVIDIA A100-SXM4-40GB & May 14, 2020 & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        MacBook Pro & 0m31.01s & 0m25.26s & 130\% & N/A & N/A & N/A & N/A & M1 Max 66GB & Nov 2021 \\ \hline
        Rivanna P100 & 0m35.732s & 0m17.253s & 0m7.595s & 470.82.01 & 11.4 & Tesla P100-PCIE & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna V100 & 0m43.160s & 0m15.510s & 0m6.894s & 470.82.01 & 11.4 & Tesla V100-SXM2 & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna K80 & 0m57.588s & 0m20.322s & 0m9.612s & 470.82.01 & 11.4 & NVIDIA TESLA K80 & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna Frontend & 1m11.535s & 1m00.780s & 0m10.352s & N/A & N/A & N/A & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\TODO{Rivann description is inomplete}

>>>>

@@

The data being used is the Southern California location data, between
32 to 36 lat -120 to -114 long. The data is recorded between
1950-2020. Each location point is is 0.1 by 0.1 degrees or ll km by ll
km in size or 2400 points in total. The points are then put into
spatial bag which are based on a bunch of different location points,
necessarily nearby spatially. Each location point has a time series
associated with it. The time series data holds magnitude, depth,
spatial position, and time. The data was accumulated into 2 week samples. 
\cite{fox2021earthquake}

The data was filtered so only significant quakes were considered 
(magnitude > 3.29). The Log Energy equation (Figure 1) was used for 
the magnitude of significant quakes inside a 2 week period.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\columnwidth]{images/Equations/log_energy.png}
    \caption{Log Energy \cite{fox2021earthquake}}
\end{figure}

The Energy Weighting equation (Figure 2) was used to average depth from quakes.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\columnwidth]{images/Equations/Q_bin.png}
    \caption{Energy Weighted \cite{fox2021earthquake}}
\end{figure}

The Multiplicity equation (Figure 3) is used to count the number of 
occurrences of significant earthquakes in a 2 week period.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.75\columnwidth]{images/Equations/Multiplicity_bin.png}
    \caption{Multiplicity \cite{fox2021earthquake}}
\end{figure}

This function maximizes the largest earthquake energy values for the 2
week period.  Magnitude averaged over the bin, all input values and
predictions are independently normalized and have a maximum modulus of
1 over all space and time values. \cite{fox2022aiforscience}

@@

\begin{table*}[!ht]
\caption{Gregors MNIST Benchmarks}\label{tab:mnist}
    \centering
      \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
    \hline
        Machine & real & user & sys & Driver & CUDA & GPU & \makecell{Date CPU \\released} & CPU & \makecell{Date CPU \\released} \\ \hline
        Gregors Machine & 0m11.534s & 0m13.914s & 0m05.186s & 510.47.03 & 11.6 & Gigabyte RTX3070 TI & May 31, 2021 & AMD 5950X & Nov 2020 \\ \hline
        Fox DGX & 0m19.987s & 5m12.991s & 0m49.266s & 450.142.00 & 11.0 & NVIDIA A100 80GB & & AMD EPYC 7742 64-Core & Aug 2019 \\ \hline
        Rivanna A100 & 0m29.263s & 0m14.585s & 0m7.399ss & 470.82.01 & 11.4 & NVIDIA A100-SXM4-40GB & May 14, 2020 & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        MacBook Pro & 0m31.01s & 0m25.26s & 130\% & N/A & N/A & N/A & N/A & M1 Max 66GB & Nov 2021 \\ \hline
        Rivanna P100 & 0m35.732s & 0m17.253s & 0m7.595s & 470.82.01 & 11.4 & Tesla P100-PCIE & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna V100 & 0m43.160s & 0m15.510s & 0m6.894s & 470.82.01 & 11.4 & Tesla V100-SXM2 & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna K80 & 0m57.588s & 0m20.322s & 0m9.612s & 470.82.01 & 11.4 & NVIDIA TESLA K80 & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rivanna Frontend & 1m11.535s & 1m00.780s & 0m10.352s & N/A & N/A & N/A & & Intel(R) Xeon(R) CPU E5-2630 v3 @ 2.40GHz & Q3  2014 \\ \hline
        Rob K & 
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\TODO{Rivanna description is incomplete}
